# 2022-03-14 - Fixed mutation rates

## Setup

```{r}
experiment_slug <- "2022-04-18-chg-rates"
working_directory <- paste0("experiments/",experiment_slug,"/analysis/")
```

### Analysis dependencies

Load all required R libraries

```{r}
library(tidyverse)
library(ggplot2)
library(scales)
library(cowplot)
library(RColorBrewer)
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
```

These analyses were knit with the following environment:

```{r}
print(version)
```

### Load data

Load summary data.

```{r}
summary_data_loc <- paste0(working_directory, "data/aggregate.csv")
summary_data <- read.csv(summary_data_loc, na.strings="NONE")

summary_data$COPY_MUT_PROB <- as.factor(
  summary_data$COPY_MUT_PROB
)
summary_data$env_chg_rate <- factor(
  summary_data$env_chg_rate,
  levels=c(
    "none",
    "30",
    "50",
    "100",
    "200",
    "300",
    "500",
    "1000",
    "2000",
    "3000",
    "5000"
  )
)
summary_data$env_condition <- as.factor(
  summary_data$env_condition
)
summary_data$env_type <- as.factor(
  summary_data$env_type
)

get_env_chg_rate_label <- function(env_chg_rate, env_type) {
  if (env_chg_rate == "none" && env_type=="consta") {
    return("none-a")
  } else if (env_chg_rate == "none" && env_type=="constb") {
    return("none-b")
  } else if (env_chg_rate=="30") {
    return("30")
  } else if (env_chg_rate=="50") {
    return("50")
  } else if (env_chg_rate=="100") {
    return("100")
  } else if (env_chg_rate=="200") {
    return("200")
  } else if (env_chg_rate=="300") {
    return("300")
  } else if (env_chg_rate=="500") {
    return("500")
  } else if (env_chg_rate=="1000") {
    return("1000")
  } else if (env_chg_rate=="2000") {
    return("2000")
  } else if (env_chg_rate=="3000") {
    return("3000")
  } else if (env_chg_rate=="5000") {
    return("5000")
  } else {
    return("unknown")
  }
}
get_env_type_label <- function(env_type) {
  if (env_type=="consta" || env_type=="constb") {
    return("const")
  } else if (env_type=="cycling") {
    return("cycling")
  } else if (env_type=="random") {
    return("random")
  }
}
get_combined_env_type_label <- function(env_type) {
  if (env_type=="consta" || env_type=="constb") {
    return("cycling+const")
  } else if (env_type=="cycling") {
    return("cycling+const")
  } else if (env_type=="random") {
    return("random")
  }
}
summary_data$env_chg_rate_label <- mapply(
  get_env_chg_rate_label,
  summary_data$env_chg_rate,
  summary_data$env_type
)
summary_data$env_chg_rate_label <- factor(
  summary_data$env_chg_rate_label,
  levels=c(
    "none-a",
    "none-b",
    "30",
    "50",
    "100",
    "200",
    "300",
    "500",
    "1000",
    "2000",
    "3000",
    "5000"
  )
)
summary_data$env_type_label <- mapply(
  get_env_type_label,
  summary_data$env_type
)
summary_data$combined_env_type_label <- mapply(
  get_combined_env_type_label,
  summary_data$env_type
)
```

Load time series data.

```{r}
time_series_data_loc <- paste0(working_directory, "data/time_series_u0-u300000.csv")
time_series_data <- read.csv(time_series_data_loc, na.strings="NONE")

time_series_data$COPY_MUT_PROB <- as.factor(
  time_series_data$COPY_MUT_PROB
)
time_series_data$env_chg_rate <- as.factor(
  time_series_data$env_chg_rate
)
time_series_data$env_condition <- as.factor(
  time_series_data$env_condition
)
time_series_data$env_type <- as.factor(
  time_series_data$env_type
)

time_series_data$env_chg_rate_label <- mapply(
  get_env_chg_rate_label,
  time_series_data$env_chg_rate,
  time_series_data$env_type
)
time_series_data$env_chg_rate_label <- factor(
  time_series_data$env_chg_rate_label,
  levels=c(
    "none-a",
    "none-b",
    "30",
    "50",
    "100",
    "200",
    "300",
    "500",
    "1000",
    "2000",
    "3000",
    "5000"
  )
)
time_series_data$env_type_label <- mapply(
  get_env_type_label,
  time_series_data$env_type
)
```

Miscellaneous setup.

```{r}
# Configure our default graphing theme
theme_set(theme_cowplot())
# Palette
cb_palette <- "Set2"
alpha <- 0.05
# Create a directory to store plots
plot_directory <- paste0(working_directory, "plots/")
dir.create(plot_directory, showWarnings=FALSE)
```

## True replication rate

### Time series

```{r}
ggplot(
    time_series_data,
    # filter(time_series_data, (update%%1000)==0),
    aes(
      x=update,
      y=avg_true_replication_rate,
      fill=env_condition,
      color=env_condition
    )
  ) +
  stat_summary(geom="line", fun=mean) +
  stat_summary(
    geom="ribbon",
    fun.data="mean_cl_boot",
    fun.args=list(conf.int=0.95),
    alpha=0.2,
    linetype=0
  ) +
  # stat_summary(
  #   geom="ribbon",
  #   fun.min=min,
  #   fun.max=max,
  #   alpha=0.2,
  #   linetype=0
  # ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  scale_y_continuous(
    trans=log10_trans()
  ) +
  facet_grid(
    COPY_MUT_PROB~env_type_label
  ) +
  theme(
    legend.position="bottom"
  )

ggsave(
  paste0(working_directory, "plots/", "avg_true_replication_rate_ot.pdf"),
  width=15,
  height=10
)
```

### Final

```{r}
ggplot(
    summary_data,
    aes(
      x=env_chg_rate_label,
      y=avg_true_replication_rate,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  # scale_fill_brewer(
  #   palette=cb_palette
  # ) +
  # scale_color_brewer(
  #   palette=cb_palette
  # ) +
  scale_y_continuous(
    trans=log10_trans()
  ) +
  facet_grid(
    COPY_MUT_PROB~env_type_label,
    scales="free_x"
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x = element_text(angle = 90),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(working_directory, "plots/", "avg_true_replication_rate.pdf")
)
```

## Final mutation rates

```{r}
ggplot(
    summary_data,
    aes(
      x=env_chg_rate_label,
      y=final_average_copy_mutation_rate,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  # scale_fill_brewer(
  #   palette=cb_palette
  # ) +
  # scale_color_brewer(
  #   palette=cb_palette
  # ) +
  # scale_y_continuous(
  #   trans=log10_trans()
  # ) +
  facet_grid(
    COPY_MUT_PROB~env_type_label,
    scales="free_x"
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x = element_text(angle = 90),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(working_directory, "plots/", "final_average_copy_mutation_rate.pdf")
)
```

```{r}
mut_rate_ot <- ggplot(
    filter(
      time_series_data,
      (update%%1000)==0
    ),
    aes(
      x=update,
      y=mutation_rates_average_copy_mutation_rate,
      fill=env_condition,
      color=env_condition
    )
  ) +
  stat_summary(geom="line", fun=mean) +
  # stat_summary(
  #   geom="ribbon",
  #   fun.data="mean_cl_boot",
  #   fun.args=list(conf.int=0.95),
  #   alpha=0.2,
  #   linetype=0
  # ) +
  stat_summary(
    geom="ribbon",
    fun.min=min,
    fun.max=max,
    alpha=0.2,
    linetype=0
  ) +
  # scale_fill_brewer(
  #   palette=cb_palette
  # ) +
  # scale_color_brewer(
  #   palette=cb_palette
  # ) +
  scale_y_continuous(
    trans=log10_trans()
  ) +
  facet_grid(
    COPY_MUT_PROB~env_type_label
  ) +
  theme(
    legend.position="bottom"
  )

ggsave(
  mut_rate_ot,
  filename=paste0(working_directory, "plots/", "average_copy_mutation_rate_ot.pdf"),
  width=15,
  height=10
)
```

## Pairwise knockout data

```{r}
pw_ko_data_loc <- paste0(working_directory, "data/pairwise_knockouts_run_summary.csv")
pw_ko_data <- read.csv(pw_ko_data_loc, na.strings="NONE")

pw_ko_data$COPY_MUT_PROB <- as.factor(
  pw_ko_data$COPY_MUT_PROB
)
pw_ko_data$env_chg_rate <- as.factor(
  pw_ko_data$env_chg_rate
)
pw_ko_data$env_condition <- as.factor(
  pw_ko_data$env_condition
)
pw_ko_data$env_type <- as.factor(
  pw_ko_data$env_type
)

pw_ko_data$env_chg_rate_label <- mapply(
  get_env_chg_rate_label,
  pw_ko_data$env_chg_rate,
  pw_ko_data$env_type
)
pw_ko_data$env_chg_rate_label <- factor(
  pw_ko_data$env_chg_rate_label,
  levels=c(
    "none-a",
    "none-b",
    "30",
    "50",
    "100",
    "200",
    "300",
    "500",
    "1000",
    "2000",
    "3000",
    "5000"
  )
)
pw_ko_data$env_type_label <- mapply(
  get_env_type_label,
  pw_ko_data$env_type
)
pw_ko_data$combined_env_type_label <- mapply(
  get_combined_env_type_label,
  pw_ko_data$env_type
)

pw_ko_data$redundant_sites_per_task <- pw_ko_data$num_redundant_task_sites / pw_ko_data$num_tasks_performed
pw_ko_data$sites_per_task <- pw_ko_data$num_task_coding_sites / pw_ko_data$num_tasks_performed
pw_ko_data$prop_multi_task_sites <- pw_ko_data$num_multi_task_sites / pw_ko_data$num_task_coding_sites

pw_ko_longer <- pivot_longer(
  pw_ko_data,
  cols=c(
    "num_and_task_coding_sites",
    "num_andnot_task_coding_sites",
    "num_nand_task_coding_sites",
    "num_not_task_coding_sites",
    "num_or_task_coding_sites",
    "num_ornot_task_coding_sites"
  ),
  names_to="task_name",
  values_to="num_sites"
)
```

### num_redundant_viability_sites

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=env_chg_rate_label,
      y=num_redundant_viability_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  # scale_fill_brewer(
  #   palette=cb_palette
  # ) +
  # scale_color_brewer(
  #   palette=cb_palette
  # ) +
  # scale_y_continuous(
  #   trans=log10_trans()
  # ) +
  facet_grid(
    combined_env_type_label~COPY_MUT_PROB,
    scales="free_x"
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(working_directory, "plots/", "num_redundant_viability_sites.pdf")
)
```

### num_viability_sites

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=env_chg_rate_label,
      y=num_viability_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  # scale_fill_brewer(
  #   palette=cb_palette
  # ) +
  # scale_color_brewer(
  #   palette=cb_palette
  # ) +
  # scale_y_continuous(
  #   trans=log10_trans()
  # ) +
  facet_grid(
    combined_env_type_label~COPY_MUT_PROB,
    scales="free_x"
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(working_directory, "plots/", "num_viability_sites.pdf")
)
```

### num_task_recovery_sites

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=env_chg_rate_label,
      y=num_task_recovery_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  # scale_fill_brewer(
  #   palette=cb_palette
  # ) +
  # scale_color_brewer(
  #   palette=cb_palette
  # ) +
  # scale_y_continuous(
  #   trans=log10_trans()
  # ) +
  facet_grid(
    combined_env_type_label~COPY_MUT_PROB,
    scales="free_x"
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(working_directory, "plots/", "num_task_recovery_sites.pdf")
)
```

### num_redundant_task_sites

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=env_chg_rate_label,
      y=num_redundant_task_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  # scale_fill_brewer(
  #   palette=cb_palette
  # ) +
  # scale_color_brewer(
  #   palette=cb_palette
  # ) +
  # scale_y_continuous(
  #   trans=log10_trans()
  # ) +
  facet_grid(
    combined_env_type_label~COPY_MUT_PROB,
    scales="free_x"
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(working_directory, "plots/", "num_redundant_task_sites.pdf")
)
```


### num_nonredundant_task_sites

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=env_chg_rate_label,
      y=num_nonredundant_task_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  # scale_fill_brewer(
  #   palette=cb_palette
  # ) +
  # scale_color_brewer(
  #   palette=cb_palette
  # ) +
  # scale_y_continuous(
  #   trans=log10_trans()
  # ) +
  facet_grid(
    combined_env_type_label~COPY_MUT_PROB,
    scales="free_x"
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(working_directory, "plots/", "num_nonredundant_task_sites.pdf")
)
```

### num_task_coding_sites

```{r}
ggplot(
    # filter(pw_ko_data,tasks_performed=="and;not;or"),
    pw_ko_data,
    aes(
      x=env_chg_rate_label,
      y=num_task_coding_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  # scale_fill_brewer(
  #   palette=cb_palette
  # ) +
  # scale_color_brewer(
  #   palette=cb_palette
  # ) +
  # scale_y_continuous(
  #   trans=log10_trans()
  # ) +
  facet_grid(
    combined_env_type_label~COPY_MUT_PROB,
    scales="free_x"
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(working_directory, "plots/", "num_task_coding_sites.pdf")
)
```

### sites_per_task

```{r}
ggplot(
    # filter(pw_ko_data,tasks_performed=="and;not;or"),
    pw_ko_data,
    aes(
      x=env_chg_rate_label,
      y=sites_per_task,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  # scale_fill_brewer(
  #   palette=cb_palette
  # ) +
  # scale_color_brewer(
  #   palette=cb_palette
  # ) +
  # scale_y_continuous(
  #   trans=log10_trans()
  # ) +
  facet_grid(
    combined_env_type_label~COPY_MUT_PROB,
    scales="free_x"
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(working_directory, "plots/", "sites_per_task.pdf")
)
```