# 2022-03-14 - Fixed mutation rates

## Setup

```{r}
experiment_slug <- "2022-03-14-fixed-mut"
working_directory <- paste0("experiments/",experiment_slug,"/analysis/")
```

### Analysis dependencies

Load all required R libraries

```{r}
library(tidyverse)
library(ggplot2)
library(scales)
library(cowplot)
library(RColorBrewer)
library(viridis)
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
```

These analyses were knit with the following environment:

```{r}
print(version)
```

### Load data for analysis

```{r}
# Run summary data
summary_data_loc <- paste0(
  working_directory,
  "data/aggregate.csv"
)
summary_data <- read.csv(
  summary_data_loc,
  na.strings="NONE"
)

# Time series data
time_series_data_loc <- paste0(
  working_directory,
  "data/time_series_u0-u300000.csv"
)
time_series_data <- read.csv(
  time_series_data_loc,
  na.strings="NONE"
)

# -- Mutational landscaping data --
# Landscape summary data (run-level)
ls2_run_summary_data_loc <- paste0(
  working_directory,
  "data/landscape_run_summary_step-2.csv"
)
ls2_run_summary_data <- read.csv(
  ls2_run_summary_data_loc,
  na.strings="NONE"
)

# Landscape task pairs cooccurrence data (pair-level, by treatment)
ls2_cooccur_data_loc <- paste0(
  working_directory,
  "data/landscape_task_cooccurrence_treatment_summary_step-2.csv"
)
ls2_cooccur_data <- read.csv(
  ls2_cooccur_data_loc,
  na.strings="NONE"
)

# Landscape task pairs cooccurrence data (pair-level, by run)
ls2_pairwise_cooccur_data_loc <- paste0(
  working_directory,
  "data/landscape_task_cooccurrence_step-2.csv"
)
ls2_pairwise_cooccur_data <- read.csv(
  ls2_pairwise_cooccur_data_loc,
  na.strings="NONE"
)

# Landscape data, distribution of mutant phenotypes
ls2_phen_dists_data_loc <- paste0(
  working_directory,
  "data/mutant_phenotype_distances_step-2.csv"
)
ls2_phen_dists_data <- read.csv(
  ls2_phen_dists_data_loc,
  na.strings="NONE"
)

# Landscape data, distribution tasks toggled
ls2_task_toggle_data_loc <- paste0(
  working_directory,
  "data/mutant_task_toggle_distribution_step-2.csv"
)
ls2_task_toggle_data <- read.csv(
  ls2_task_toggle_data_loc,
  na.strings="NONE"
)

# -- Knockout analysis data --
# Pairwise knockout summary data (by run)
pw_ko_data_loc <- paste0(
  working_directory,
  "data/pairwise_knockouts_run_summary.csv"
)
pw_ko_data <- read.csv(
  pw_ko_data_loc,
  na.strings="NONE"
)
```

Define data formatting functions, common factor levels

```{r}
get_env_chg_rate_label <- function(env_chg_rate, env_type) {
  if (env_chg_rate == "none" && env_type=="consta") {
    return("none-a")
  } else if (env_chg_rate == "none" && env_type=="constb") {
    return("none-b")
  } else if (env_chg_rate=="30") {
    return("30")
  } else if (env_chg_rate=="300") {
    return("300")
  } else if (env_chg_rate=="3000") {
    return("3000")
  } else {
    return("unknown")
  }
}

get_env_type_label <- function(env_type) {
  if (env_type=="consta" || env_type=="constb") {
    return("const")
  } else if (env_type=="cycling") {
    return("cycling")
  } else if (env_type=="random") {
    return("random")
  }
}

get_final_mut_rate <- function(seed) {
  filtered_data <- filter(summary_data, RANDOM_SEED==seed)
  return(filtered_data$final_average_copy_mutation_rate)
}

get_dom_match_score_env_a <- function(seed) {
  filtered_data <- filter(summary_data, RANDOM_SEED==seed)
  return(filtered_data$dom_match_score_env_a)
}

env_chg_rate_factor_levels <- c(
  "none",
  "30",
  "300",
  "3000"
)
env_chg_rate_label_factor_levels <- c(
  "none-a",
  "none-b",
  "30",
  "300",
  "3000"
)

```

Data cleanup/formatting

```{r}
# ---- summary_data ----
summary_data$COPY_MUT_PROB <- as.factor(
  summary_data$COPY_MUT_PROB
)
summary_data$env_chg_rate <- factor(
  summary_data$env_chg_rate,
  env_chg_rate_factor_levels
)
summary_data$env_condition <- as.factor(
  summary_data$env_condition
)
summary_data$env_type <- as.factor(
  summary_data$env_type
)
summary_data$env_chg_rate_label <- mapply(
  get_env_chg_rate_label,
  summary_data$env_chg_rate,
  summary_data$env_type
)
summary_data$env_chg_rate_label <- factor(
  summary_data$env_chg_rate_label,
  env_chg_rate_label_factor_levels
)
summary_data$env_type_label <- mapply(
  get_env_type_label,
  summary_data$env_type
)

# ---- time_series_data ----
time_series_data$COPY_MUT_PROB <- as.factor(
  time_series_data$COPY_MUT_PROB
)
time_series_data$env_chg_rate <- as.factor(
  time_series_data$env_chg_rate
)
time_series_data$env_condition <- as.factor(
  time_series_data$env_condition
)
time_series_data$env_type <- as.factor(
  time_series_data$env_type
)

time_series_data$env_chg_rate_label <- mapply(
  get_env_chg_rate_label,
  time_series_data$env_chg_rate,
  time_series_data$env_type
)
time_series_data$env_chg_rate_label <- factor(
  time_series_data$env_chg_rate_label,
  env_chg_rate_label_factor_levels
)
time_series_data$env_type_label <- mapply(
  get_env_type_label,
  time_series_data$env_type
)

# ---- ls2_run_summary_data ----
ls2_run_summary_data$COPY_MUT_PROB <- as.factor(
  ls2_run_summary_data$COPY_MUT_PROB
)
ls2_run_summary_data$env_chg_rate <- as.factor(
  ls2_run_summary_data$env_chg_rate
)
ls2_run_summary_data$env_condition <- as.factor(
  ls2_run_summary_data$env_condition
)
ls2_run_summary_data$env_type <- as.factor(
  ls2_run_summary_data$env_type
)
ls2_run_summary_data$env_chg_rate_label <- mapply(
  get_env_chg_rate_label,
  ls2_run_summary_data$env_chg_rate,
  ls2_run_summary_data$env_type
)
ls2_run_summary_data$env_chg_rate_label <- factor(
  ls2_run_summary_data$env_chg_rate_label,
  levels = env_chg_rate_label_factor_levels
)
ls2_run_summary_data$env_type_label <- mapply(
  get_env_type_label,
  ls2_run_summary_data$env_type
)

# ---- ls2_cooccur_data ----
ls2_cooccur_data$COPY_MUT_PROB <- as.factor(
  ls2_cooccur_data$COPY_MUT_PROB
)
ls2_cooccur_data$env_chg_rate <- as.factor(
  ls2_cooccur_data$env_chg_rate
)
ls2_cooccur_data$env_condition <- as.factor(
  ls2_cooccur_data$env_condition
)
ls2_cooccur_data$env_type <- as.factor(
  ls2_cooccur_data$env_type
)
ls2_cooccur_data$task_1_id <- as.factor(
  ls2_cooccur_data$task_1_id
)
ls2_cooccur_data$task_2_id <- as.factor(
  ls2_cooccur_data$task_2_id
)
ls2_cooccur_data$env_chg_rate_label <- mapply(
  get_env_chg_rate_label,
  ls2_cooccur_data$env_chg_rate,
  ls2_cooccur_data$env_type
)
ls2_cooccur_data$env_chg_rate_label <- factor(
  ls2_cooccur_data$env_chg_rate_label,
  levels=env_chg_rate_label_factor_levels
)
ls2_cooccur_data$env_type_label <- mapply(
  get_env_type_label,
  ls2_cooccur_data$env_type
)

# ---- ls2_pairwise_cooccur_data ----
ls2_pairwise_cooccur_data$COPY_MUT_PROB <- as.factor(
  ls2_pairwise_cooccur_data$COPY_MUT_PROB
)
ls2_pairwise_cooccur_data$env_chg_rate <- as.factor(
  ls2_pairwise_cooccur_data$env_chg_rate
)
ls2_pairwise_cooccur_data$env_condition <- as.factor(
  ls2_pairwise_cooccur_data$env_condition
)
ls2_pairwise_cooccur_data$env_type <- as.factor(
  ls2_pairwise_cooccur_data$env_type
)
ls2_pairwise_cooccur_data$task_1_id <- as.factor(
  ls2_pairwise_cooccur_data$task_1_id
)
ls2_pairwise_cooccur_data$task_2_id <- as.factor(
  ls2_pairwise_cooccur_data$task_2_id
)
ls2_pairwise_cooccur_data$env_chg_rate_label <- mapply(
  get_env_chg_rate_label,
  ls2_pairwise_cooccur_data$env_chg_rate,
  ls2_pairwise_cooccur_data$env_type
)
ls2_pairwise_cooccur_data$env_chg_rate_label <- factor(
  ls2_pairwise_cooccur_data$env_chg_rate_label,
  levels=env_chg_rate_label_factor_levels
)
ls2_pairwise_cooccur_data$env_type_label <- mapply(
  get_env_type_label,
  ls2_pairwise_cooccur_data$env_type
)

# ---- ls2_phen_dists_data ----
ls2_phen_dists_data$COPY_MUT_PROB <- as.factor(
  ls2_phen_dists_data$COPY_MUT_PROB
)
ls2_phen_dists_data$env_chg_rate <- as.factor(
  ls2_phen_dists_data$env_chg_rate
)
ls2_phen_dists_data$env_condition <- as.factor(
  ls2_phen_dists_data$env_condition
)
ls2_phen_dists_data$env_type <- as.factor(
  ls2_phen_dists_data$env_type
)
ls2_phen_dists_data$distance <- factor(
  ls2_phen_dists_data$distance,
  levels=c(
    -1,
    0,
    1,
    2,
    3,
    4,
    5,
    6
  )
)
# Simplify replicate IDs (start at 0 for each treatment)
ls_simplify_replicate_id <- function(e, m, rep_id) {
  treatment_data <- filter(
    ls2_phen_dists_data,
    (env_condition==e) & (COPY_MUT_PROB==m)
  )
  rep_ids <- as.integer(levels(factor(treatment_data$replicate_id)))
  rep_id_map <- as.data.frame(rep_ids)
  rep_id_map$order <- order(rep_id_map$rep_ids)
  return(filter(rep_id_map, rep_ids==rep_id)$order)
}
ls2_phen_dists_data$rep_id <- mapply(
  ls_simplify_replicate_id,
  ls2_phen_dists_data$env_condition,
  ls2_phen_dists_data$COPY_MUT_PROB,
  ls2_phen_dists_data$replicate_id
)
ls2_phen_dists_data$rep_id <- as.factor(
  ls2_phen_dists_data$rep_id
)
ls2_phen_dists_data$replicate_id <- as.factor(
  ls2_phen_dists_data$replicate_id
)
ls2_phen_dists_data$RANDOM_SEED <- as.factor(
  ls2_phen_dists_data$RANDOM_SEED
)
ls2_phen_dists_data$env_chg_rate_label <- mapply(
  get_env_chg_rate_label,
  ls2_phen_dists_data$env_chg_rate,
  ls2_phen_dists_data$env_type
)
ls2_phen_dists_data$env_chg_rate_label <- factor(
  ls2_phen_dists_data$env_chg_rate_label,
  levels=env_chg_rate_label_factor_levels
)
ls2_phen_dists_data$env_type_label <- mapply(
  get_env_type_label,
  ls2_phen_dists_data$env_type
)

# ---- ls2_task_toggle_data ----
ls2_task_toggle_data$COPY_MUT_PROB <- as.factor(
  ls2_task_toggle_data$COPY_MUT_PROB
)
ls2_task_toggle_data$env_chg_rate <- as.factor(
  ls2_task_toggle_data$env_chg_rate
)
ls2_task_toggle_data$env_condition <- as.factor(
  ls2_task_toggle_data$env_condition
)
ls2_task_toggle_data$env_type <- as.factor(
  ls2_task_toggle_data$env_type
)
ls2_task_toggle_data$num_tasks_toggled <- factor(
  ls2_task_toggle_data$num_tasks_toggled,
  levels=c(
    -1,
    0,
    1,
    2,
    3,
    4,
    5,
    6
  )
)

ls2_task_toggle_data$RANDOM_SEED <- as.factor(
  ls2_task_toggle_data$RANDOM_SEED
)
ls2_task_toggle_data$env_chg_rate_label <- mapply(
  get_env_chg_rate_label,
  ls2_task_toggle_data$env_chg_rate,
  ls2_task_toggle_data$env_type
)
ls2_task_toggle_data$env_chg_rate_label <- factor(
  ls2_task_toggle_data$env_chg_rate_label,
  levels=env_chg_rate_label_factor_levels
)

# ---- pw_ko_data ----
pw_ko_data$COPY_MUT_PROB <- as.factor(
  pw_ko_data$COPY_MUT_PROB
)
pw_ko_data$env_chg_rate <- as.factor(
  pw_ko_data$env_chg_rate
)
pw_ko_data$env_condition <- as.factor(
  pw_ko_data$env_condition
)
pw_ko_data$env_type <- as.factor(
  pw_ko_data$env_type
)
pw_ko_data$env_chg_rate_label <- mapply(
  get_env_chg_rate_label,
  pw_ko_data$env_chg_rate,
  pw_ko_data$env_type
)
pw_ko_data$env_chg_rate_label <- factor(
  pw_ko_data$env_chg_rate_label,
  levels=env_chg_rate_label_factor_levels
)
pw_ko_data$env_type_label <- mapply(
  get_env_type_label,
  pw_ko_data$env_type
)

pw_ko_data$redundant_sites_per_task <-
  pw_ko_data$num_redundant_task_sites / pw_ko_data$num_tasks_performed
pw_ko_data$sites_per_task <-
  pw_ko_data$num_task_coding_sites / pw_ko_data$num_tasks_performed
pw_ko_data$prop_multi_task_sites <-
  pw_ko_data$num_multi_task_sites / pw_ko_data$num_task_coding_sites

pw_ko_longer <- pivot_longer(
  pw_ko_data,
  cols=c(
    "num_and_task_coding_sites",
    "num_andnot_task_coding_sites",
    "num_nand_task_coding_sites",
    "num_not_task_coding_sites",
    "num_or_task_coding_sites",
    "num_ornot_task_coding_sites"
  ),
  names_to="task_name",
  values_to="num_sites"
)
```

Define focal conditions.

```{r}
focal_mut_rates <- c(0.0001, 0.001, 0.01, 0.0316)
focal_envs <- c(
  "env-consta",
  "env-constb",
  "env-cycling_rate-300",
  "env-random_rate-300"
)

env_breaks<-c("consta", "constb", "cycling", "random")
env_labels<-c("Const-A", "Const-B", "Cyclic", "Random")

env_facets <- c(
  "env-consta"="Const-A",
  "env-constb"="Const-B",
  "env-cycling_rate-300"="Cyclic",
  "env-random_rate-300"="Random"
)
env_facet_labeller <- function(variable, value) {
  return(env_facets[value])
}
```

Filter down to focal data

```{r}
summary_data <- filter(
  summary_data,
  COPY_MUT_PROB%in%focal_mut_rates & env_condition%in%focal_envs
)
time_series_data <- filter(
  time_series_data,
  COPY_MUT_PROB%in%focal_mut_rates & env_condition%in%focal_envs
)
pw_ko_data <- filter(
  pw_ko_data,
  COPY_MUT_PROB%in%focal_mut_rates & env_condition%in%focal_envs
)
pw_ko_longer <- filter(
  pw_ko_data,
  COPY_MUT_PROB%in%focal_mut_rates & env_condition%in%focal_envs
)

ls2_run_summary_data <- filter(
  ls2_run_summary_data,
  COPY_MUT_PROB%in%focal_mut_rates & env_condition%in%focal_envs
)

ls2_cooccur_data <- filter(
  ls2_cooccur_data,
  COPY_MUT_PROB%in%focal_mut_rates & env_condition%in%focal_envs
)

ls2_pairwise_cooccur_data <- filter(
  ls2_pairwise_cooccur_data,
  COPY_MUT_PROB%in%focal_mut_rates & env_condition%in%focal_envs
)

ls2_phen_dists_data <- filter(
  ls2_phen_dists_data,
  COPY_MUT_PROB%in%focal_mut_rates & env_condition%in%focal_envs
)

ls2_task_toggle_data <- filter(
  ls2_task_toggle_data,
  COPY_MUT_PROB%in%focal_mut_rates & env_condition%in%focal_envs
)
```

### Miscellaneous setup

```{r}
# Configure our default graphing theme
theme_set(theme_cowplot())
# Palette
cb_palette <- "Set2"
alpha <- 0.05
# Create a directory to store plots
plot_directory <- paste0(working_directory, "plots/mut-effect-on-variation/")
dir.create(plot_directory, showWarnings=FALSE)
```

## True replication rate

```{r}
ggplot(
    filter(
      time_series_data,
      (update%%1000)==0
    ),
    aes(
      x=update,
      y=avg_true_replication_rate,
      fill=env_condition,
      color=env_condition
    )
  ) +
  stat_summary(geom="line", fun=mean) +
  stat_summary(
    geom="ribbon",
    fun.data="mean_cl_boot",
    fun.args=list(conf.int=0.95),
    alpha=0.2,
    linetype=0
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~COPY_MUT_PROB,
    nrow = 1
  ) +
  theme(
    legend.position="bottom"
  )

ggsave(
  paste0(plot_directory, "avg_true_replication_rate_ot.pdf"),
  width=15,
  height=10
)
```

## Dominant lineage length (genotypes)

```{r}
ggplot(
    summary_data,
    aes(
      x=COPY_MUT_PROB,
      y=dom_lineage_length_genotypes,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  scale_y_continuous(
    trans=log10_trans()
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "dom_lineage_length_genotypes.pdf")
)
```

## Phylogeny analyses

### Phylogenetic diversity

```{r}
ggplot(
    summary_data,
    aes(
      x=COPY_MUT_PROB,
      y=phylo_current_phylogenetic_diversity,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(
    plot_directory,
    "phylo_current_phylogenetic_diversity.pdf"
  )
)
```

### MRCA changes

```{r}
ggplot(
    summary_data,
    aes(
      x=COPY_MUT_PROB,
      y=phylo_mrca_changes,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "phylo_mrca_changes.pdf")
)
```

### MRCA depth

```{r}
ggplot(
    summary_data,
    aes(
      x=COPY_MUT_PROB,
      y=phylo_mrca_depth / dom_lineage_length_genotypes,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  scale_y_continuous(
    trans=log10_trans()
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "phylo_mrca_depth.pdf")
)
```

## Knockout analyses

### Redundant viability sites

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=COPY_MUT_PROB,
      y=num_redundant_viability_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "num_redundant_viability_sites.pdf")
)
```

### Viability sites

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=COPY_MUT_PROB,
      y=num_viability_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "num_viability_sites.pdf")
)
```

### Task recovery sites

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=COPY_MUT_PROB,
      y=num_task_recovery_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "num_task_recovery_sites.pdf")
)
```

### Redundant task sites

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=COPY_MUT_PROB,
      y=num_redundant_task_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "num_redundant_task_sites.pdf")
)
```

### Task codings sites

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=COPY_MUT_PROB,
      y=num_task_coding_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "num_task_coding_sites.pdf")
)
```

### Average sites per task

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=COPY_MUT_PROB,
      y=sites_per_task,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "sites_per_task.pdf")
)
```

### Sites per task

```{r}
ggplot(
    filter(
      pw_ko_longer,
      num_sites>0
    ),
    aes(
      x=COPY_MUT_PROB,
      y=num_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_grid(
    env_type~task_name
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "pw_num_task_sites_by_task.pdf"),
  height=10,
  width=20
)
```

### Multi-task sites (overlap)

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=COPY_MUT_PROB,
      y=prop_multi_task_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "prop_multi_task_sites.pdf")
)
```

## Mutational landscape analyses

### Viable mutants

```{r}
ggplot(
    ls2_run_summary_data,
    aes(
      x=COPY_MUT_PROB,
      y=prop_viable,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "prop_viable_mutants_step-2.pdf")
)
```

### Unique phenotypes in landscape

```{r}
ggplot(
    ls2_run_summary_data,
    aes(
      x=COPY_MUT_PROB,
      y=num_unique_viable_phenotypes,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "num_unique_viable_phenotypes_step-2.pdf")
)
```

### Entropy of phenotypes in landscape

```{r}
ggplot(
    ls2_run_summary_data,
    aes(
      x=COPY_MUT_PROB,
      y=entropy_viable_phenotypes,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "entropy_viable_phenotypes_step-2.pdf")
)
```

### Average distance from mutant phenotype to ancestral phenotype

```{r}
ggplot(
    ls2_run_summary_data,
    aes(
      x=COPY_MUT_PROB,
      y=avg_dist_to_ancestor,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )

ggsave(
  paste0(plot_directory, "avg_dist_to_ancestor_step-2.pdf")
)
```

### Number of viable mutants that flip to alternate environment

```{r}
ggplot(
    ls2_run_summary_data,
    aes(
      x=COPY_MUT_PROB,
      y=num_viable_mutants_flip_env,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  scale_y_continuous(
    trans=pseudo_log_trans(sigma=1,base=10),
    breaks=c(0, 10, 100, 1000, 10000, 100000, 1000000)
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )

ggsave(
  paste0(plot_directory, "num_viable_mutants_flip_env_step-2.pdf")
)
```

### Number that flip versus proportion that don't change

```{r}
get_num_mutants_same_phenotype <- function(seed) {
  toggle_data <- filter(
    ls2_task_toggle_data,
    (num_tasks_toggled==0) & (RANDOM_SEED == seed)
  )
  return(toggle_data$num_mutants)
}

# ls2_phen_dists_data
get_num_mutants_alt_adapted_phenotype <- function(seed) {
  adapted_data <- filter(
    ls2_phen_dists_data,
    (distance %in% c("0", "1")) & (RANDOM_SEED == seed)
  )
  num_mutants <- sum(adapted_data$count_env_b)
  return(num_mutants)
}

ls2_run_summary_data$num_mutants_same_phenotype <- mapply(
  get_num_mutants_same_phenotype,
  ls2_run_summary_data$RANDOM_SEED
)
ls2_run_summary_data$prop_viable_same_phenotype <- ls2_run_summary_data$num_mutants_same_phenotype / ls2_run_summary_data$num_viable
ls2_run_summary_data$prop_viable_alt_phenotype <- ls2_run_summary_data$num_viable_mutants_flip_env / ls2_run_summary_data$num_viable


ls2_run_summary_data$num_mutants_alt_adapted_phen <- mapply(
  get_num_mutants_alt_adapted_phenotype,
  ls2_run_summary_data$RANDOM_SEED
)
ls2_run_summary_data$prop_viable_alt_adapted_phen <- ls2_run_summary_data$num_mutants_alt_adapted_phen / ls2_run_summary_data$num_viable
ls2_run_summary_data$prop_viable_improve_b_phen <- ls2_run_summary_data$num_viable_mutants_improve_env_b / ls2_run_summary_data$num_viable

ggplot(
    filter(
      ls2_run_summary_data,
      env_type%in%c("cycling")
    ),
    aes(
      x=prop_viable_same_phenotype,
      # y=prop_viable_alt_phenotype,
      # y=num_viable_mutants_improve_env_b / num_viable,
      y=num_mutants_alt_adapted_phen / num_viable,
      fill=COPY_MUT_PROB,
      color=COPY_MUT_PROB
    )
  ) +
  geom_point(
    mapping=aes(
      color=COPY_MUT_PROB,
      fill=COPY_MUT_PROB
    ),
  ) +
  geom_smooth(
    method="lm"
    # fill="#0077ff76"
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  # scale_y_continuous(
  #   trans=pseudo_log_trans(sigma=1,base=10)
    # breaks=c(0, 10, 100, 1000, 10000, 100000, 1000000)
  # ) +
  # scale_x_continuous(
  #   trans=pseudo_log_trans(sigma=1,base=10)
  #   # breaks=c(0, 10, 100, 1000, 10000, 100000, 1000000)
  # ) +
  facet_wrap(
    ~env_type
  ) +
  theme(
    legend.position="bottom",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1)
    # panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "prop_alt_adapted_vs_prop_same_phen-2.pdf")
)
```

```{r}
temp_data <- pivot_longer(
  ls2_run_summary_data,
  cols=c(
    "prop_viable_improve_b_phen",
    "prop_viable_alt_adapted_phen"
  ),
  names_to="improvement_level",
  values_to="prop"
)

ggplot(
    filter(
      temp_data,
      env_type%in%c("cycling")
    ),
    aes(
      x=prop_viable_same_phenotype,
      # y=prop_viable_alt_phenotype,
      # y=num_viable_mutants_improve_env_b / num_viable,
      y=prop,
      linetype=improvement_level,
      fill=COPY_MUT_PROB,
      color=COPY_MUT_PROB
    )
  ) +
  geom_point(
    mapping=aes(
      color=COPY_MUT_PROB,
      fill=COPY_MUT_PROB,
      shape=improvement_level
    ),
  ) +
  geom_smooth(
    method="lm"
    # fill="#0077ff76"
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type
  ) +
  theme(
    legend.position="bottom",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1)
    # panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "out.pdf")
)
```

### Number of viable mutants that gain tasks

```{r}
ggplot(
    ls2_run_summary_data,
    aes(
      x=COPY_MUT_PROB,
      y=num_viable_mutants_gain_tasks,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )

ggsave(
  paste0(plot_directory, "num_viable_mutants_gain_tasks_step-2.pdf")
)
```

### Number of viable mutants that gain multiple tasks

```{r}
ggplot(
    ls2_run_summary_data,
    aes(
      x=COPY_MUT_PROB,
      y=num_viable_mutants_gain_multiple_tasks,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  scale_y_continuous(
    trans=pseudo_log_trans(sigma=1,base=10),
    breaks=c(0, 10, 100, 1000, 10000, 100000)
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )

ggsave(
  paste0(plot_directory, "num_viable_mutants_gain_multiple_tasks_step-2.pdf")
)
```

### Number of viable mutants that lose tasks

```{r}
ggplot(
    ls2_run_summary_data,
    aes(
      x=COPY_MUT_PROB,
      y=num_viable_mutants_lose_tasks,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )

ggsave(
  paste0(plot_directory, "num_viable_mutants_lose_tasks_step-2.pdf")
)
```

### Number of viable mutants that lose multiple tasks

```{r}
ggplot(
    ls2_run_summary_data,
    aes(
      x=COPY_MUT_PROB,
      y=num_viable_mutants_lose_multiple_tasks,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )

ggsave(
  paste0(plot_directory, "num_viable_mutants_lose_multiple_tasks_step-2.pdf")
)
```

### Total NPMI

```{r}
ggplot(
    ls2_run_summary_data,
    aes(
      x=COPY_MUT_PROB,
      y=total_npmi,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  geom_hline(
    yintercept=0,
    linetype="dashed",
    size=0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~env_type,
    nrow = 1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )

ggsave(
  paste0(plot_directory, "total_npmi_step-2.pdf")
)
```

### Total NPMI by task pair

```{r}
ggplot(
    filter(
      ls2_pairwise_cooccur_data,
      env_type=="cycling"
    ),
    aes(
      x=task_2_id,
      y=npmi,
      fill=COPY_MUT_PROB,
      color=COPY_MUT_PROB
    )
  ) +
  geom_point(
    size = .5,
    alpha = 0.8
  ) +
  stat_summary(
    geom="errorbar",
    fun.data="mean_cl_boot",
    fun.args=list(conf.int=0.95),
    color="black"
    # alpha=0.2
  ) +
  geom_hline(
    yintercept=0,
    linetype="dashed",
    size=0.5
  ) +
  facet_grid(
    task_1_id~COPY_MUT_PROB,
    scales="free_x"
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )

ggsave(
  paste0(plot_directory, "total_npmi_pairwise_step-2.pdf")
)
```

### Distribution of mutant phenotypes

```{r}
ggplot(
    ls2_phen_dists_data,
    aes(
      x=rep_id,
      y=count_env_a,
      fill=distance
    )
  ) +
  geom_bar(
    position="stack",
    stat="identity"
  ) +
  scale_fill_manual(
    name="Distance to ENV-A",
    values=c("#000000", viridis(n=7, alpha=1, direction=-1))
  ) +
  facet_grid(
    env_type~COPY_MUT_PROB,
    scales="free_x"
  ) +
  theme(
    legend.position="bottom",
    axis.text.x=element_text(size=10)
  )

ggsave(
  paste0(plot_directory, "mutant_phen_dist_env_a_step-2.pdf"),
  width=15,
  height=18
)
```

## Manuscript figures

### Mutation rate

```{r}
fig_num_mutants_that_flip_by_mut_rate <-
  ggplot(
    filter(
      ls2_run_summary_data,
      env_condition=="env-cycling_rate-300"
    ),
    aes(
      x=COPY_MUT_PROB,
      y=num_viable_mutants_flip_env
    )
  ) +
  geom_flat_violin(
    fill="#8DA0CB",
    scale="area",
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    fill="#8DA0CB",
    color="#8DA0CB",
    position = position_jitter(width = .15),
    size = 1,
    alpha = 0.8
  ) +
  geom_boxplot(
    fill="#8DA0CB",
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_y_continuous(
    name="Mutants adapted to\nalternate environment (log scale)",
    # trans=log10_trans()
    trans=pseudo_log_trans(sigma=1,base=10),
    breaks=c(0, 10, 100, 1000, 10000, 100000, 1000000)
  ) +
  scale_x_discrete(
    name="Mutation rate"
  ) +
  facet_wrap(
    ~env_condition,
    nrow=1,
    labeller=as_labeller(env_facets)
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14)
  )
fig_num_mutants_that_flip_by_mut_rate


ggsave(
  filename=paste0(plot_directory, "2022-03-14-mutants-fip-env-by-mut-rate-figure.pdf"),
  plot=fig_num_mutants_that_flip_by_mut_rate,
  width=5,
  height=4
  # base_height=6
  # base_asp=2
)
```

### High mutation rate result in more robust genotypes

```{r}
limits<-c(0.2, 1.0)
```

#### Viability

```{r}
fig_prop_viable <-
  ggplot(
    ls2_run_summary_data,
    aes(
      x=COPY_MUT_PROB,
      y=prop_viable,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    scale="area",
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = 1,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  # stat_summary(
  #   geom="line",
  #   fun="mean",
  #   group=1
  # ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  scale_x_discrete(
    name="Mutation rate"
  ) +
  scale_y_continuous(
    name="Proportion viable"
    # limits=limits
  ) +
  facet_wrap(
    ~env_condition,
    nrow=1,
    labeller=as_labeller(env_facets)
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14)
  )
fig_prop_viable
```

#### Task phenotype

```{r}
fig_phenotypic_profile_robustness <-
  ggplot(
    filter(
      ls2_task_toggle_data,
      (num_tasks_toggled==0) &
      COPY_MUT_PROB%in%focal_mut_rates & env_condition%in%focal_envs
    ),
    aes(
      x=COPY_MUT_PROB,
      y=prop_of_viable,
      # y=num_mutants,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = 1,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  # geom_hline(
  #   yintercept=0,
  #   linetype="dashed",
  #   size=0.5
  # ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  scale_y_continuous(
    name="Proportion viable with same phenotype"
  ) +
  scale_x_discrete(
    name="Mutation rate"
  ) +
  facet_wrap(
    ~env_condition,
    nrow=1,
    labeller=as_labeller(env_facets)
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14)
  )
fig_phenotypic_profile_robustness
```

#### Combined

```{r}
grid <- plot_grid(
  fig_prop_viable +
    scale_y_continuous(
      name="\nProportion viable"
    ) +
    theme(
      axis.title.x = element_blank(),
      axis.text.x = element_blank()
    ),
  fig_phenotypic_profile_robustness +
    scale_y_continuous(
      name="Proportion viable\nwith same phenotype"
    ),
  nrow=2,
  ncol=1,
  labels="auto",
  axis="r"
)
grid

ggsave(
  filename=paste0(plot_directory, "2022-03-14-robustness-figure.pdf"),
  plot=grid,
  width=12,
  height=6
  # base_height=6
  # base_asp=2
)
```

### Robustness

#### Number of coding sites

```{r}
fig_num_task_coding_sites <-
  ggplot(
    pw_ko_data,
    aes(
      x=COPY_MUT_PROB,
      y=sites_per_task,
      # y=num_task_coding_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = 1,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  scale_y_continuous(
    name="Avg. sites per task"
  ) +
  scale_x_discrete(
    name="Mutation rate"
  ) +
  facet_wrap(
    ~env_condition,
    nrow=1,
    labeller=as_labeller(env_facets)
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14)
  )
fig_num_task_coding_sites
```

#### Redundancy

```{r}
fig_num_redundant_task_sites <-
  ggplot(
    pw_ko_data,
    aes(
      x=COPY_MUT_PROB,
      # y=num_redundant_task_sites,
      y=redundant_sites_per_task,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = 1,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  scale_y_continuous(
    name="Redundant sites per task"
  ) +
  scale_x_discrete(
    name="Mutation rate"
  ) +
  facet_wrap(
    ~env_condition,
    nrow=1,
    labeller=as_labeller(env_facets)
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14)
  )
fig_num_redundant_task_sites
```

#### Function Overlap

```{r}
fig_prop_multi_task_sites <-
  ggplot(
    pw_ko_data,
    aes(
      x=COPY_MUT_PROB,
      y=prop_multi_task_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = 1,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  scale_y_continuous(
    name="Proportion shared task sites"
  ) +
  scale_x_discrete(
    name="Mutation rate"
  ) +
  facet_wrap(
    ~env_condition,
    nrow=1,
    labeller=as_labeller(env_facets)
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14)
  )
fig_prop_multi_task_sites
```

#### Combined

```{r}

ggsave(
  filename=paste0(plot_directory, "2022-03-14-num-redundant-sites.pdf"),
  plot=fig_num_redundant_task_sites,
  width=12,
  height=4
)
ggsave(
  filename=paste0(plot_directory, "2022-03-14-prop-multi-task-sites.pdf"),
  plot=fig_prop_multi_task_sites,
  width=12,
  height=4
)
ggsave(
  filename=paste0(plot_directory, "2022-03-14-sites-per-task.pdf"),
  plot=fig_num_task_coding_sites,
  width=12,
  height=4
)
```