# 2022-03-14 - Fixed mutation rates

## Setup

```{r}
experiment_slug <- "2022-03-14-fixed-mut"
working_directory <- paste0("experiments/",experiment_slug,"/analysis/")
```

### Analysis dependencies

Load all required R libraries

```{r}
library(tidyverse)
library(ggplot2)
library(scales)
library(cowplot)
library(RColorBrewer)
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
```

These analyses were knit with the following environment:

```{r}
print(version)
```

### Load data for analysis

```{r}
# Run summary data
summary_data_loc <- paste0(
  working_directory,
  "data/aggregate.csv"
)
summary_data <- read.csv(
  summary_data_loc,
  na.strings="NONE"
)

# Time series data
time_series_data_loc <- paste0(
  working_directory,
  "data/time_series_u0-u300000.csv"
)
time_series_data <- read.csv(
  time_series_data_loc,
  na.strings="NONE"
)

# -- Mutational landscaping data --
# Landscape summary data (run-level)
ls2_run_summary_data_loc <- paste0(
  working_directory,
  "data/landscape_run_summary_step-2.csv"
)
ls2_run_summary_data <- read.csv(
  ls2_run_summary_data_loc,
  na.strings="NONE"
)

# Landscape task pairs cooccurrence data (pair-level, by treatment)
ls2_cooccur_data_loc <- paste0(
  working_directory,
  "data/landscape_task_cooccurrence_treatment_summary_step-2.csv"
)
ls2_cooccur_data <- read.csv(
  ls2_cooccur_data_loc,
  na.strings="NONE"
)

# Landscape task pairs cooccurrence data (pair-level, by run)
ls2_pairwise_cooccur_data_loc <- paste0(
  working_directory,
  "data/landscape_task_cooccurrence_step-2.csv"
)
ls2_pairwise_cooccur_data <- read.csv(
  ls2_pairwise_cooccur_data_loc,
  na.strings="NONE"
)

# Landscape data, distribution of mutant phenotypes
ls2_phen_dists_data_loc <- paste0(
  working_directory,
  "data/mutant_phenotype_distances_step-2.csv"
)
ls2_phen_dists_data <- read.csv(
  ls2_phen_dists_data_loc,
  na.strings="NONE"
)

# Landscape data, distribution tasks toggled
ls2_task_toggle_data_loc <- paste0(
  working_directory,
  "data/mutant_task_toggle_distribution_step-2.csv"
)
ls2_task_toggle_data <- read.csv(
  ls2_task_toggle_data_loc,
  na.strings="NONE"
)

# -- Knockout analysis data --
# Pairwise knockout summary data (by run)
pw_ko_data_loc <- paste0(
  working_directory,
  "data/pairwise_knockouts_run_summary.csv"
)
pw_ko_data <- read.csv(
  pw_ko_data_loc,
  na.strings="NONE"
)
```

Define data formatting functions, common factor levels

```{r}
get_env_chg_rate_label <- function(env_chg_rate, env_type) {
  if (env_chg_rate == "none" && env_type=="consta") {
    return("none-a")
  } else if (env_chg_rate == "none" && env_type=="constb") {
    return("none-b")
  } else if (env_chg_rate=="30") {
    return("30")
  } else if (env_chg_rate=="300") {
    return("300")
  } else if (env_chg_rate=="3000") {
    return("3000")
  } else {
    return("unknown")
  }
}

get_env_type_label <- function(env_type) {
  if (env_type=="consta" || env_type=="constb") {
    return("const")
  } else if (env_type=="cycling") {
    return("cycling")
  } else if (env_type=="random") {
    return("random")
  }
}

# Simplify replicate IDs (start at 0 for each treatment)
ls_simplify_replicate_id <- function(ref_data, e, m, rep_id) {
  treatment_data <- filter(
    ref_data,
    (env_condition==e) & (COPY_MUT_PROB==m)
  )
  rep_ids <- as.integer(levels(factor(treatment_data$replicate_id)))
  rep_id_map <- as.data.frame(rep_ids)
  rep_id_map$order <- order(rep_id_map$rep_ids)
  return(filter(rep_id_map, rep_ids==rep_id)$order)
}

get_final_mut_rate <- function(seed) {
  filtered_data <- filter(summary_data, RANDOM_SEED==seed)
  return(filtered_data$final_average_copy_mutation_rate)
}

get_dom_match_score_env_a <- function(seed) {
  filtered_data <- filter(summary_data, RANDOM_SEED==seed)
  return(filtered_data$dom_match_score_env_a)
}

env_chg_rate_factor_levels <- c(
  "none",
  "30",
  "300",
  "3000"
)
env_chg_rate_label_factor_levels <- c(
  "none-a",
  "none-b",
  "30",
  "300",
  "3000"
)

```

Data cleanup/formatting

```{r}
# ---- summary_data ----
summary_data$COPY_MUT_PROB <- as.factor(
  summary_data$COPY_MUT_PROB
)
summary_data$env_chg_rate <- factor(
  summary_data$env_chg_rate,
  env_chg_rate_factor_levels
)
summary_data$env_condition <- as.factor(
  summary_data$env_condition
)
summary_data$env_type <- as.factor(
  summary_data$env_type
)
summary_data$env_chg_rate_label <- mapply(
  get_env_chg_rate_label,
  summary_data$env_chg_rate,
  summary_data$env_type
)
summary_data$env_chg_rate_label <- factor(
  summary_data$env_chg_rate_label,
  env_chg_rate_label_factor_levels
)
summary_data$env_type_label <- mapply(
  get_env_type_label,
  summary_data$env_type
)

# ---- time_series_data ----
time_series_data$COPY_MUT_PROB <- as.factor(
  time_series_data$COPY_MUT_PROB
)
time_series_data$env_chg_rate <- as.factor(
  time_series_data$env_chg_rate
)
time_series_data$env_condition <- as.factor(
  time_series_data$env_condition
)
time_series_data$env_type <- as.factor(
  time_series_data$env_type
)

time_series_data$env_chg_rate_label <- mapply(
  get_env_chg_rate_label,
  time_series_data$env_chg_rate,
  time_series_data$env_type
)
time_series_data$env_chg_rate_label <- factor(
  time_series_data$env_chg_rate_label,
  env_chg_rate_label_factor_levels
)
time_series_data$env_type_label <- mapply(
  get_env_type_label,
  time_series_data$env_type
)

# ---- ls2_run_summary_data ----


# ---- ls2_cooccur_data ----


# ---- ls2_pairwise_cooccur_data ----


# ---- ls2_phen_dists_data ----


# ---- ls2_task_toggle_data ----


# ---- pw_ko_data ----
pw_ko_data$COPY_MUT_PROB <- as.factor(
  pw_ko_data$COPY_MUT_PROB
)
pw_ko_data$env_chg_rate <- as.factor(
  pw_ko_data$env_chg_rate
)
pw_ko_data$env_condition <- as.factor(
  pw_ko_data$env_condition
)
pw_ko_data$env_type <- as.factor(
  pw_ko_data$env_type
)
pw_ko_data$env_chg_rate_label <- mapply(
  get_env_chg_rate_label,
  pw_ko_data$env_chg_rate,
  pw_ko_data$env_type
)
pw_ko_data$env_chg_rate_label <- factor(
  pw_ko_data$env_chg_rate_label,
  levels=env_chg_rate_label_factor_levels
)
pw_ko_data$env_type_label <- mapply(
  get_env_type_label,
  pw_ko_data$env_type
)

pw_ko_data$redundant_sites_per_task <-
  pw_ko_data$num_redundant_task_sites / pw_ko_data$num_tasks_performed
pw_ko_data$sites_per_task <-
  pw_ko_data$num_task_coding_sites / pw_ko_data$num_tasks_performed
pw_ko_data$prop_multi_task_sites <-
  pw_ko_data$num_multi_task_sites / pw_ko_data$num_task_coding_sites

pw_ko_longer <- pivot_longer(
  pw_ko_data,
  cols=c(
    "num_and_task_coding_sites",
    "num_andnot_task_coding_sites",
    "num_nand_task_coding_sites",
    "num_not_task_coding_sites",
    "num_or_task_coding_sites",
    "num_ornot_task_coding_sites"
  ),
  names_to="task_name",
  values_to="num_sites"
)
```

Define focal conditions.

```{r}
focal_mut_rate <- 0.001
focal_envs <- c(
  "env-consta",
  "env-constb",
  "env-cycling_rate-300",
  "env-random_rate-300"
)
env_breaks<-c("consta", "constb", "cycling", "random")
env_labels<-c("Const-A", "Const-B", "Cyclic", "Random")

env_facets <- c(
  "env-consta"="Const-A",
  "env-constb"="Const-B",
  "env-cycling_rate-300"="Cyclic",
  "env-random_rate-300"="Random"
)
env_facet_labeller <- function(variable, value) {
  return(env_facets[value])
}
```

Filter down to focal data

```{r}
summary_data <- filter(
  summary_data,
  COPY_MUT_PROB==focal_mut_rate & env_condition%in%focal_envs
)
time_series_data <- filter(
  time_series_data,
  COPY_MUT_PROB==focal_mut_rate & env_condition%in%focal_envs
)
pw_ko_data <- filter(
  pw_ko_data,
  COPY_MUT_PROB==focal_mut_rate & env_condition%in%focal_envs
)
pw_ko_longer <- filter(
  pw_ko_data,
  COPY_MUT_PROB==focal_mut_rate & env_condition%in%focal_envs
)
```

### Miscellaneous setup

```{r}
# Configure our default graphing theme
theme_set(theme_cowplot())
# Palette
cb_palette <- "Set2"
alpha <- 0.05
# Create a directory to store plots
plot_directory <- paste0(working_directory, "plots-env-effect-on-variation/")
dir.create(plot_directory, showWarnings=FALSE)
```

## True replication rate

### Early in experiment

```{r}
ggplot(
    filter(time_series_data, update < 10000),
    aes(
      x=update,
      y=avg_true_replication_rate,
      fill=env_condition,
      color=env_condition
    )
  ) +
  stat_summary(geom="line", fun=mean) +
  stat_summary(
    geom="ribbon",
    fun.data="mean_cl_boot",
    fun.args=list(conf.int=0.95),
    alpha=0.2,
    linetype=0
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  theme(
    legend.position="bottom"
  )

ggsave(
  paste0(plot_directory, "avg_true_replication_rate_ot-early.pdf"),
  width=15,
  height=10
)
```

### Entire experiment

```{r}
ggplot(
    time_series_data,
    aes(
      x=update,
      y=avg_true_replication_rate,
      fill=env_condition,
      color=env_condition
    )
  ) +
  stat_summary(geom="line", fun=mean) +
  stat_summary(
    geom="ribbon",
    fun.data="mean_cl_boot",
    fun.args=list(conf.int=0.95),
    alpha=0.2,
    linetype=0
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  theme(
    legend.position="bottom"
  )

ggsave(
  paste0(plot_directory, "avg_true_replication_rate_ot.pdf"),
  width=15,
  height=10
)
```

## Dominant lineage length (genotypes)

```{r}
ggplot(
    summary_data,
    aes(
      x=env_type,
      y=dom_lineage_length_genotypes,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  scale_y_continuous(
    trans=log10_trans()
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    # axis.text.x = element_text(angle = 90),
    panel.border = element_rect(color = "grey", fill=NA, size=1.5)
  )
ggsave(
  paste0(plot_directory, "dom_lineage_length_genotypes.pdf")
)
```

## Phylogeny analyses

### Phylogenetic diversity

```{r}
ggplot(
    summary_data,
    aes(
      x=env_type,
      y=phylo_current_phylogenetic_diversity,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14)
  )
ggsave(
  paste0(
    plot_directory,
    "phylo_current_phylogenetic_diversity.pdf"
  )
)
```

### MRCA changes

```{r}
ggplot(
    summary_data,
    aes(
      x=env_type,
      y=phylo_mrca_changes,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  # scale_y_continuous(
  #   trans=log10_trans()
  # ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14)
  )
ggsave(
  paste0(plot_directory, "phylo_mrca_changes.pdf")
)
```

### MRCA depth

```{r}
ggplot(
    summary_data,
    aes(
      x=env_type,
      y=phylo_mrca_depth / dom_lineage_length_genotypes,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  scale_y_continuous(
    trans=log10_trans()
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14)
  )
ggsave(
  paste0(plot_directory, "phylo_mrca_depth.pdf")
)
```

## Knockout analyses

### Redundant viability sites

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=env_type,
      y=num_redundant_viability_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1)
  )
ggsave(
  paste0(plot_directory, "num_redundant_viability_sites.pdf")
)
```

### Viability sites

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=env_type,
      y=num_viability_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1)
  )
ggsave(
  paste0(plot_directory, "num_viability_sites.pdf")
)
```

```{r}
kruskal.test(
  formula=num_viability_sites~env_type,
  data=pw_ko_data
)
```

### Task recovery sites

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=env_type,
      y=num_task_recovery_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1)
  )
ggsave(
  paste0(plot_directory, "num_task_recovery_sites.pdf")
)
```

```{r}
kruskal.test(
  formula=num_task_recovery_sites~env_type,
  data=pw_ko_data
)
```

### Redundant task sites

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=env_type,
      y=num_redundant_task_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1)
  )
ggsave(
  paste0(plot_directory, "num_redundant_task_sites.pdf")
)
```

```{r}
kruskal.test(
  formula=num_redundant_task_sites~env_type,
  data=pw_ko_data
)
```

### Task codings sites

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=env_type,
      y=num_task_coding_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1)
  )
ggsave(
  paste0(plot_directory, "num_task_coding_sites.pdf")
)
```

### Average sites per task

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=env_type,
      y=sites_per_task,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1)
  )
ggsave(
  paste0(plot_directory, "sites_per_task.pdf")
)
```

### Sites per task

```{r}
ggplot(
    filter(
      pw_ko_longer,
      num_sites>0
    ),
    aes(
      x=env_type,
      y=num_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  facet_wrap(
    ~task_name,
    nrow=1
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1)
  )
ggsave(
  paste0(plot_directory, "pw_num_task_sites_by_task.pdf"),
  height=10,
  width=20
)
```

### Multi-task sites (overlap)

```{r}
ggplot(
    pw_ko_data,
    aes(
      x=env_type,
      y=prop_multi_task_sites,
      fill=env_condition
    )
  ) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    alpha = .8,
    adjust=1.5
  ) +
  geom_point(
    mapping=aes(color=env_condition),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8
  ) +
  geom_boxplot(
    width = .1,
    outlier.shape = NA,
    alpha = 0.5
  ) +
  scale_fill_brewer(
    palette=cb_palette
  ) +
  scale_color_brewer(
    palette=cb_palette
  ) +
  theme(
    legend.position="none",
    axis.text=element_text(size=14),
    axis.text.x=element_text(angle=45,hjust=1)
  )
ggsave(
  paste0(plot_directory, "prop_multi_task_sites.pdf")
)
```

```{r}
kruskal.test(
  formula=prop_multi_task_sites~env_type,
  data=pw_ko_data
)
```

## Mutational landscape analyses




## Manuscript figures



